Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-05-30 raspi_journal.tex
Small contribution to multicore

The idea of \ac{TSNC} is therefore to gradually increase the coding density
as the decoderes \ac{DOF} increases. This enables TSNC to save a lot of
complexity particulary in the beginning of transmissions, but also to
tailor the coding delay. I.e. approximate the number of coded packets a
decoder needs to receive to decode a generation of $g$ packets. We call
this number the budget, $B$.

@@

>>>>

The idea of \ac{TSNC} is therefore to gradually increase the coding density
as the decoderes \ac{DOF} increases. This enables TSNC to save a lot of
complexity particulary in the beginning of transmissions, but also to
tailor the coding delay. I.e., approximate the number of coded packets a
decoder needs to receive to decode a generation of $g$ packets. We call
this number the budget, $B$.

@@

\subsection{Network Coding Implementation for Multicore Architectures}
\label{sub:implementation-multicore}

The operations needed to encode and decode the data are, in general, similar. To
encode packets, the encoder needs to perform the matrix multiplication
$\textbf{C} = \textbf{V} \cdot \textbf{P}$. On the other hand, decoding the
information requires the decoder to find $\textbf{V}^{-1}$ and to perform the
matrix multiplication $\textbf{P} = \textbf{V}^{-1} \cdot \textbf{C}$. In both
cases, a matrix multiplication is needed. Therefore, to make a practical
implementation of network coding, it is valuable to find a way to optimize the
matrix multiplications operations for multicore architectures.

Some algorithms implement the decoding combining the matrix inversion and the
matrix multiplication, e.g., performing the Gauss-Jordan algorithm over the
coding matrix $\textbf{V}$ while performing, in parallel, row operations on the
coded data $\textbf{C}$. The parallelization of such operations provide speeds
up that are limited for small block sizes ($\leq 2048$ bytes). The reason is
that to operate in a parallel fashion over the same coded packet $C_i$ requires
strained synchronization.
